Validation question:

What are Jimmy Reed, Skip James, Elmore James and Big Bill Broonzy best known as?

Prompt:

Answer: Eleonore Roosevelt
Question: On which Caribbean island did Princess Diana spend he first Christmas after her divorce was announced?
Answer: Barbuda Dependency, Antigua and Barbuda
Question: Who wrote the song Momma Told Me Not To Come?
Answer: Randy Newman
Question: What is the distance between bases on a little league baseball field?
Answer: sixty  distance
Question: Which NASA space probe was launched to Venus in 1989?
Answer: List of things named for Ferdinand Magellan
Question: Which member of the Monkees came from Washington DC?
Answer: Peter Tork
Question: Who was the woman sentenced to six years in jail after the murder of Stompei Seipi?
Answer: Winnifred Mandela
Question: Which Italian fashion designer was murdered on the orders of his ex-wife?
Answer: House of Gucci

Validation question:

For which movie did Katharine Hepburn win her second Oscar?

Prompt:

Question: Which African country is sandwiched between Ghana and Benin?
Answer: Religion in Togo
Question: Which African country is bordered by Benin, Ghana, Ivory Coast, Niger, and Mali?
Answer: Burkina Faso
Question: Which country mainly makes up the Horn of Africa?
Answer: Somolia
Question: In The Banana Splits what sort of animal was Snorky?
Answer: Elephantineness
Question: What are the two main arms of the River Nile called?
Answer: Blue Nile and White Nile
Question: Name the East African country which lies on the equator.
Answer: Prehistory of Kenya
Question: What are the international registration letters of a vehicle from Algeria?
Answer: DZ (disambiguation)
Question: Banting and Best pioneered the use of what?
Answer: Insullin
